Carrying out Latent Profile Analysis in Accordance With Best Practices: A Tutorial Using the tidyLPA R package

### 2020-01-30 paper.rmd
update

``` {r, compare-mclust, eval = FALSE}
curry_mac_solutions <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))
```

@@

``` {r, compare-mplus, eval = TRUE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9, package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))
```

>>>>

``` {r, compare-mclust, eval = FALSE}
curry_mac_solutions <- curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9) %>%
  compare_solutions(statistics = c("AIC", "BIC"))

3Best model according to AIC is Model 6 with 7 classes.
# Best model according to BIC is Model 6 with 2 classes.

#An analytic hierarchy process, based on the fit indices AIC, AWE, BIC, CLC, and KIC (Akogul & Erisoglu, 2017), suggests the best solution is Model 6 with 2 classes.
```

@@

``` {r, compare-mplus, eval = TRUE}
curry_mac %>% 
  select(KinshipR:PossessionR, 
         KinshipJ:PossessionJ) %>% 
  estimate_profiles(models = c(1, 2, 3, 6),
                    n_profiles = 1:9, package = "mplus") %>%
  compare_solutions(statistics = c("AIC", "BIC"))

# Best model according to AIC is Model 6 with 4 classes.
# Best model according to BIC is Model 6 with 2 classes.

# An analytic hierarchy process, based on the fit indices AIC, AWE, BIC, CLC, and KIC (Akogul & Erisoglu, 2017), suggests the best solution is Model 6 with 2 classes.
```

```{r}

```
